---
title: "CapstoneProject"
author: "Vivek Appadurai"
date: "February 20, 2016"
output:
    html_document:
        keep_md: true
---

## Loading Libraries

```{r, message = FALSE}
library(dplyr)
library(ggplot2)
library(scales)
library(reshape2)
library(knitr)
library(gridExtra)
library(ROCR)
library(e1071)
library(brglm)
library(logistf)
```

## Reading Data

```{r}
variableInfo <- read.table("Names.txt", 
                           header = T, 
                           sep = "\t", 
                           fill = NA, 
                           quote = "",
                           stringsAsFactors = FALSE)
L0 <- read.table("L0.txt", header = T, sep = "\t", fill = NA, quote = "")
L1 <- read.table("L1.txt", header = F, sep = "\t", fill = NA, quote = "")
L2 <- read.table("L2.txt", header = F, sep = "\t", fill = NA, quote = "")
L3 <- read.table("L3.txt", header = F, sep = "\t", fill = NA, quote = "")
L4 <- read.table("L4.txt", header = F, sep = "\t", fill = NA, quote = "")
ticDataTraining <- read.table("ticdata2000.txt", 
                              header = F, 
                              sep = "\t", 
                              fill = NA, 
                              quote = "", 
                              stringsAsFactors = FALSE)
ticDataTest <- read.table("ticeval2000.txt", 
                          header = F, 
                          sep = "\t", 
                          fill = NA, 
                          quote = "",
                          stringsAsFactors = FALSE)
targets <- read.table("tictgts2000.txt",
                              header = F,
                              stringsAsFactors = FALSE)
```

## Data Cleaning

```{r}
colNames <- variableInfo %>% select(Name) %>% unlist()
names(ticDataTraining) <- colNames
ticDataTraining$Set <- "Training"
ticDataTest$CARAVAN <- targets$V1
names(ticDataTest) <- colNames
ticDataTest$Set <- "Test"
ticData <- rbind(ticDataTraining, ticDataTest)
ticData <- left_join(ticData, L0, by = c("MOSTYPE"= "Value"))
ticData <- ticData %>% rename(MOSTYPE2 = Label)
names(L2) <- c("MOSHOOFD","MOSHOOFD2")
ticData <- left_join(ticData, L2)

ticDataTraining <- ticData %>% filter(Set == "Training")
ticDataTraining <- ticDataTraining %>% mutate(totalCaravanPolicies = sum(CARAVAN))
```

## Exploratory Data Analysis

Since the number of caravan policy holders within the training data is very low (348/5822 or apprxomiately 6%), 
its best to explore the assocaitions within the data by looking at the fraction of policy holders at each value 
for the varaibles along with the proportion of population at that particular value

```{r, include = FALSE}
ticDataTraining <- ticDataTraining %>% 
    group_by(MAANTHUI) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHomesOwned <- ggplot(data = ticDataTraining, aes(x = MAANTHUI)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MAANTHUI), 1)) +
    xlab("Number of Homes Owned") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>% 
    group_by(MGEMOMV) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseHoldSize <- ggplot(data = ticDataTraining, aes(x = MGEMOMV)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGEMOMV), 1)) +
    xlab("Average Household Size") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>% 
    group_by(MGEMLEEF) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

PlotAvgAge <- ggplot(data = ticDataTraining, aes(x = MGEMLEEF)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGEMLEEF), 1)) +
    xlab("Average Age") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>% 
    group_by(MGODRK) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotRomanCatholics <- ggplot(data = ticDataTraining, aes(x = MGODRK)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGODRK), 1)) +
    xlab("Roman Catholics") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>% 
    group_by(MGODPR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotProtestants <- ggplot(data = ticDataTraining, aes(x = MGODPR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGODPR), 1)) +
    xlab("Protestants") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>% 
    group_by(MGODOV) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotOtherReligion <- ggplot(data = ticDataTraining, aes(x = MGODOV)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGODOV), 1)) +
    xlab("Other Religion") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MGODGE) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNoReligion <- ggplot(data = ticDataTraining, aes(x = MGODGE)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MGODGE), 1)) +
    xlab("No Religion") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MRELGE) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotMarried <- ggplot(data = ticDataTraining, aes(x = MRELGE)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MRELGE), 1)) +
    xlab("Married") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MRELSA) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotLivingTogether <- ggplot(data = ticDataTraining, aes(x = MRELSA)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MRELSA), 1)) +
    xlab("Living Together") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MRELOV) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotOtherRelation <- ggplot(data = ticDataTraining, aes(x = MRELOV)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MRELOV), 1)) +
    xlab("Other Relation") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MFALLEEN) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSingles <- ggplot(data = ticDataTraining, aes(x = MFALLEEN)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MFALLEEN), 1)) +
    xlab("Singles") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MFGEKIND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseholdNoChild <- ggplot(data = ticDataTraining, aes(x = MFGEKIND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MFGEKIND), 1)) +
    xlab("Household No Children") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MFWEKIND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseholdWithChild <- ggplot(data = ticDataTraining, aes(x = MFWEKIND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MFWEKIND), 1)) +
    xlab("Household With Children") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MOPLHOOG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseholdHighEd <- ggplot(data = ticDataTraining, aes(x = MOPLHOOG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MOPLHOOG), 1)) +
    xlab("High Level Education") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MOPLMIDD) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseholdMidEd <- ggplot(data = ticDataTraining, aes(x = MOPLMIDD)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MOPLMIDD), 1)) +
    xlab("Mid Level Education") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MOPLLAAG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHouseholdLowEd <- ggplot(data = ticDataTraining, aes(x = MOPLLAAG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MOPLLAAG), 1)) +
    xlab("Low Level Education") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERHOOG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotHighStatus <- ggplot(data = ticDataTraining, aes(x = MBERHOOG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERHOOG), 1)) +
    xlab("High Status") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERZELF) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotEntrepreneur <- ggplot(data = ticDataTraining, aes(x = MBERZELF)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERZELF), 1)) +
    xlab("Entrepreneur") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERBOER) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotFarmer <- ggplot(data = ticDataTraining, aes(x = MBERBOER)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERBOER), 1)) +
    xlab("Farmer") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERMIDD) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotMidManagement <- ggplot(data = ticDataTraining, aes(x = MBERMIDD)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERMIDD), 1)) +
    xlab("Middle Management") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERARBG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSkilledLabor <- ggplot(data = ticDataTraining, aes(x = MBERARBG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERARBG), 1)) +
    xlab("Skilled Laborers") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MBERARBO) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotUnskilledLabor <- ggplot(data = ticDataTraining, aes(x = MBERARBO)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MBERARBO), 1)) +
    xlab("Unskilled Laborers") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MSKA) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialA <- ggplot(data = ticDataTraining, aes(x = MSKA)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MSKA), 1)) +
    xlab("Social Class A") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MSKB1) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialB1 <- ggplot(data = ticDataTraining, aes(x = MSKB1)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MSKB1), 1)) +
    xlab("Social Class B1") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MSKB2) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialB2 <- ggplot(data = ticDataTraining, aes(x = MSKB2)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MSKB2), 1)) +
    xlab("Social Class B2") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MSKC) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialC <- ggplot(data = ticDataTraining, aes(x = MSKC)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MSKC), 1)) +
    xlab("Social Class C") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MSKD) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialD <- ggplot(data = ticDataTraining, aes(x = MSKD)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MSKD), 1)) +
    xlab("Social Class D") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MHHUUR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotRentHouse <- ggplot(data = ticDataTraining, aes(x = MHHUUR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MHHUUR), 1)) +
    xlab("Rented House") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MHKOOP) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotOwnHome <- ggplot(data = ticDataTraining, aes(x = MHKOOP)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MHKOOP), 1)) +
    xlab("Home Owners") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MAUT1) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotOneCar <- ggplot(data = ticDataTraining, aes(x = MAUT1)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MAUT1), 1)) +
    xlab("Owns One Car") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MAUT2) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotTwoCars <- ggplot(data = ticDataTraining, aes(x = MAUT2)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MAUT2), 1)) +
    xlab("Owns Two Cars") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MAUT0) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNoCar <- ggplot(data = ticDataTraining, aes(x = MAUT0)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MAUT0), 1)) +
    xlab("No Car Owned") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MZFONDS) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNHS <- ggplot(data = ticDataTraining, aes(x = MZFONDS)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MZFONDS), 1)) +
    xlab("National Health Service") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MZPART) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPHS <- ggplot(data = ticDataTraining, aes(x = MZPART)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MZPART), 1)) +
    xlab("Private Health Insurance") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINKM30) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotIncome30k <- ggplot(data = ticDataTraining, aes(x = MINKM30)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINKM30), 1)) +
    xlab("Income < 30k") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINK3045) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotIncome30_45k <- ggplot(data = ticDataTraining, aes(x = MINK3045)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINK3045), 1)) +
    xlab("30k < Income < 45k") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINK4575) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotIncome45_75k <- ggplot(data = ticDataTraining, aes(x = MINK4575)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINK4575), 1)) +
    xlab("45k < Income < 75k") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINK7512) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotIncome75k_122k <- ggplot(data = ticDataTraining, aes(x = MINK7512)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINK7512), 1)) +
    xlab("75k < Income < 122k") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINK123M) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotIncome123k <- ggplot(data = ticDataTraining, aes(x = MINK123M)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINK123M), 1)) +
    xlab("Income > 122k") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MINKGEM) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotAvgIncome <- ggplot(data = ticDataTraining, aes(x = MINKGEM)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MINKGEM), 1)) +
    xlab("Average Income Populations") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(MKOOPKLA) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPurchasingPower <- ggplot(data = ticDataTraining, aes(x = MKOOPKLA)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$MKOOPKLA), 1)) +
    xlab("Purchasing Power") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AWAPART) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyIns <- ggplot(data = ticDataTraining, aes(x = AWAPART)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AWAPART), 1)) +
    xlab("No. of 3rd Party Insurances") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PWAPART) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyInsCont <- ggplot(data = ticDataTraining, aes(x = PWAPART)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PWAPART), 1)) +
    xlab("3rd Party Insurance Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AWABEDR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyInsFirm <- ggplot(data = ticDataTraining, aes(x = AWABEDR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AWABEDR), 1)) +
    xlab("No. of 3rd Party Insurances for FIRMS") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PWABEDR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyInsFirmCont <- ggplot(data = ticDataTraining, aes(x = PWABEDR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PWABEDR), 2)) +
    xlab("3rd Party Insurance Contributions for Firms") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AWALAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyInsAgri <- ggplot(data = ticDataTraining, aes(x = AWALAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AWALAND), 1)) +
    xlab("No. of 3rd Party Insurances for Agriculture") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PWALAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotNumThirdPartyInsAgriCont <- ggplot(data = ticDataTraining, aes(x = PWALAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PWALAND), 1)) +
    xlab("3rd Party Insurance Contributions - Agriculture") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(APERSAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotCarPolicy <- ggplot(data = ticDataTraining, aes(x = APERSAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$APERSAUT), 1)) +
    xlab("No. of Car Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PPERSAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotCarPolicyCont <- ggplot(data = ticDataTraining, aes(x = PPERSAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PPERSAUT), 4)) +
    xlab("Car Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ABESAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotVanPolicy <- ggplot(data = ticDataTraining, aes(x = ABESAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ABESAUT), 1)) +
    xlab("No. of Delivery Van Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PBESAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotVanPolicyCont <- ggplot(data = ticDataTraining, aes(x = PBESAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PBESAUT), 2)) +
    xlab("Van Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AMOTSCO) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotScooterPolicy <- ggplot(data = ticDataTraining, aes(x = AMOTSCO)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AMOTSCO), 1)) +
    xlab("No. of Scooter Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PMOTSCO) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotScooterPolicyCont <- ggplot(data = ticDataTraining, aes(x = PMOTSCO)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PMOTSCO), 4)) +
    xlab("Scooter Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AVRAAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotLorryPolicy <- ggplot(data = ticDataTraining, aes(x = AVRAAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AVRAAUT), 1)) +
    xlab("No. of Scooter Policies * Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PVRAAUT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotLorryPolicyCont <- ggplot(data = ticDataTraining, aes(x = PVRAAUT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PVRAAUT), 2)) +
    xlab("Lorry Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AAANHANG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotTrailerPolicy <- ggplot(data = ticDataTraining, aes(x = AAANHANG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AAANHANG), 1)) +
    xlab("No. of Trailer Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PAANHANG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotTrailerPolicyCont <- ggplot(data = ticDataTraining, aes(x = PAANHANG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PAANHANG), 1)) +
    xlab("Trailer Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ATRACTOR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotTractorPolicy <- ggplot(data = ticDataTraining, aes(x = ATRACTOR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ATRACTOR), 1)) +
    xlab("No. of Tractor Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PTRACTOR) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotTractorPolicyCont <- ggplot(data = ticDataTraining, aes(x = PTRACTOR)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PTRACTOR), 2)) +
    xlab("Tractor Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AWERKT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotAgriMachinePolicy <- ggplot(data = ticDataTraining, aes(x = AWERKT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AWERKT), 1)) +
    xlab("No. of Agricultural Machine Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PWERKT) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotAgriMachinePolicyCont <- ggplot(data = ticDataTraining, aes(x = PWERKT)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PWERKT), 2)) +
    xlab("Agricultural Machine Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ABROM) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotMopedPolicy <- ggplot(data = ticDataTraining, aes(x = ABROM)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ABROM), 1)) +
    xlab("No. of Moped Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PBROM) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotMopedPolicyCont <- ggplot(data = ticDataTraining, aes(x = PBROM)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PBROM), 1)) +
    xlab("Moped Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ALEVEN) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotLifePolicy <- ggplot(data = ticDataTraining, aes(x = ALEVEN)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ALEVEN), 1)) +
    xlab("No. of Life Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PLEVEN) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotLifePolicyCont <- ggplot(data = ticDataTraining, aes(x = PLEVEN)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 4) +
    scale_x_continuous(breaks = seq(0, max(ticData$PLEVEN), 4)) +
    xlab("Life Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(APERSONG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPvtAccidentPolicy <- ggplot(data = ticDataTraining, aes(x = APERSONG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$APERSONG), 1)) +
    xlab("No. of Private Accident Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PPERSONG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPvtAccidentPolicyCont <- ggplot(data = ticDataTraining, aes(x = PPERSONG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PPERSONG), 1)) +
    xlab("Private Accident Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AGEZONG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotFamAccidentPolicy <- ggplot(data = ticDataTraining, aes(x = AGEZONG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AGEZONG), 1)) +
    xlab("No. of Family Accident Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PGEZONG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotFamAccidentPolicyCont <- ggplot(data = ticDataTraining, aes(x = PGEZONG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PGEZONG), 1)) +
    xlab("Family Accident Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AWAOREG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotDisabilityPolicy <- ggplot(data = ticDataTraining, aes(x = AWAOREG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AWAOREG), 1)) +
    xlab("No. of Disability Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PWAOREG) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotDisabilityPolicyCont <- ggplot(data = ticDataTraining, aes(x = PWAOREG)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PWAOREG), 1)) +
    xlab("Disability Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ABRAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotFirePolicy <- ggplot(data = ticDataTraining, aes(x = ABRAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ABRAND), 1)) +
    xlab("No. of Fire Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PBRAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotFirePolicyCont <- ggplot(data = ticDataTraining, aes(x = PBRAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PBRAND), 1)) +
    xlab("Fire Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AZEILPL) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSurfPolicy <- ggplot(data = ticDataTraining, aes(x = AZEILPL)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AZEILPL), 1)) +
    xlab("No. of SurfBoard Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PZEILPL) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSurfPolicyCont <- ggplot(data = ticDataTraining, aes(x = PZEILPL)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PZEILPL), 1)) +
    xlab("SurfBoard Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(APLEZIER) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotBoatPolicy <- ggplot(data = ticDataTraining, aes(x = APLEZIER)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$APLEZIER), 1)) +
    xlab("No. of Boat Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PPLEZIER) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotBoatPolicyCont <- ggplot(data = ticDataTraining, aes(x = PPLEZIER)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PPLEZIER), 1)) +
    xlab("Boat Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AFIETS) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotBicyclePolicy <- ggplot(data = ticDataTraining, aes(x = AFIETS)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AFIETS), 1)) +
    xlab("No. of Bicycle Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PFIETS) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotBicyclePolicyCont <- ggplot(data = ticDataTraining, aes(x = PFIETS)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PFIETS), 1)) +
    xlab("Bicycle Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(AINBOED) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPropertyPolicy <- ggplot(data = ticDataTraining, aes(x = AINBOED)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$AINBOED), 1)) +
    xlab("No. of Property Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PINBOED) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotPropertyPolicyCont <- ggplot(data = ticDataTraining, aes(x = PINBOED)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PINBOED), 1)) +
    xlab("Property Policies Contributions") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(ABYSTAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialPolicy <- ggplot(data = ticDataTraining, aes(x = ABYSTAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$ABYSTAND), 1)) +
    xlab("No. of Social Security Policies") +
    ylab("Proportion") +
    theme_bw()

ticDataTraining <- ticDataTraining %>%
    group_by(PBYSTAND) %>%
    mutate(percent_caravan = sum(CARAVAN) / totalCaravanPolicies) %>%
    ungroup()

plotSocialPolicyCont <- ggplot(data = ticDataTraining, aes(x = PBYSTAND)) +
    geom_bar(aes(y = ..count../sum(..count..))) +
    geom_point(aes(y = percent_caravan)) +
    geom_line(aes(y = percent_caravan), linetype = 2) +
    scale_x_continuous(breaks = seq(0, max(ticData$PBYSTAND), 1)) +
    xlab("Social Security Policies Contributions") +
    ylab("Proportion") +
    theme_bw()
```

#### Plotting Using Grid Arrange

```{r, fig.width = 12, fig.height = 60}
grid.arrange(plotHomesOwned, plotHouseHoldSize, PlotAvgAge, plotRomanCatholics, plotProtestants, plotOtherReligion,
             plotNoReligion, plotMarried, plotLivingTogether, plotOtherRelation, plotSingles, plotHouseholdNoChild,
             plotHouseholdWithChild, plotHouseholdHighEd, plotHouseholdMidEd, plotHouseholdLowEd, plotHighStatus,
             plotEntrepreneur, plotFarmer, plotMidManagement, plotSkilledLabor, plotUnskilledLabor, plotSocialA,
             plotSocialB1, plotSocialB2, plotSocialC, plotSocialD, plotRentHouse, plotOwnHome, plotOneCar, 
             plotTwoCars, plotNoCar, plotNHS, plotPHS, plotIncome30k, plotIncome30_45k, plotIncome45_75k, 
             plotIncome75k_122k, plotIncome123k, plotAvgIncome, plotPurchasingPower, plotNumThirdPartyIns,
             plotNumThirdPartyInsCont, plotNumThirdPartyInsFirm, plotNumThirdPartyInsFirmCont, plotNumThirdPartyInsAgri,
             plotNumThirdPartyInsAgriCont, plotCarPolicy, plotCarPolicyCont, plotVanPolicy, plotVanPolicyCont,
             plotScooterPolicy, plotScooterPolicyCont, plotLorryPolicy, plotLorryPolicyCont, plotTrailerPolicy,
             plotTrailerPolicyCont, plotTractorPolicy, plotTractorPolicyCont, plotAgriMachinePolicy,
             plotAgriMachinePolicyCont, plotMopedPolicy, plotMopedPolicyCont, plotLifePolicy, plotLifePolicyCont,
             plotPvtAccidentPolicy, plotPvtAccidentPolicyCont, plotFamAccidentPolicy, plotFamAccidentPolicyCont,
             plotDisabilityPolicy, plotDisabilityPolicyCont, plotFirePolicy, plotFirePolicyCont, plotSurfPolicy,
             plotSurfPolicyCont, plotBoatPolicy, plotBoatPolicyCont, plotBicyclePolicy, plotBicyclePolicyCont,
             plotPropertyPolicy, plotPropertyPolicyCont, plotSocialPolicy, plotSocialPolicyCont, ncol = 2)
```

#### Observations:

From the plots the following conditions imply a higher proportion of caravan policy owners than expected:

1. Zipcodes with a less number of low level educated people
2. Zipcodes with very high status people
3. Zipcodes with NO FARMERS
4. Zipcodes with low number of laborers (skilled & unskilled)
5. Zipcodes with low number of people belonging to social classes C & D
6. Zipcodes having a very high number of Home Owners
7. Zipcodes with low or no rented homes
8. Zipcodes having a high car ownership
9. Zipcodes having little to no population with income < 30k
10. Zipcodes with average income households
11. Zipcodes with high purchasing power >= 6
12. Individuals that have a private third party insurance
13. Individuals with high contributions to third party insurance
14. Individuals with one or more car policy
15. Individuals with high contributions to their car policies
16. Individuals with Fire Insurance Policy
17. Individuals making high contributions to fire insurance policies

The above factors are worth further investigation to draw more concrete trends

```{r}
ggplot(ticDataTraining, aes(x = APERSAUT, y = PPERSAUT, color = as.factor(CARAVAN))) +
    geom_jitter() + 
    xlab("Num. Car Policies") +
    ylab("Contributions") +
    theme_bw() +
    scale_x_continuous(breaks =seq(0, max(ticData$APERSAUT), 1))
```

The plot indicates that people who have a car policy tend to contribute significantly towards it.

```{r}
ggplot(ticDataTraining, aes(x = AWAPART, y = PWAPART, color = as.factor(CARAVAN))) +
    geom_jitter() + 
    xlab("Private Third Party Insurance") +
    ylab("Contributions") +
    theme_bw() +
    scale_x_continuous(breaks =seq(0, max(ticData$AWAPART), 1))
```

```{r}
ggplot(ticDataTraining, aes(x = ABRAND, y = PBRAND, color = as.factor(CARAVAN))) +
    geom_jitter() + 
    xlab("Num. Fire Policies") +
    ylab("Contributions") +
    theme_bw() +
    scale_x_continuous(breaks =seq(0, max(ticData$ABRAND), 1))
```

### Building a Logistic Regression Model

```{r}
ticDataTraining$CARAVAN <- as.factor(ticDataTraining$CARAVAN)
ticDataTest$CARAVAN <- as.factor(ticDataTest$CARAVAN)

ticDataLogitModel <- glm(data = ticDataTraining, CARAVAN ~ 
                             (APERSAUT == 1 & PPERSAUT > 5) +
#                             APERSAUT +
                             PPERSAUT +
#                             ABRAND +
                             PBRAND +
#                             AWAPART +
                             PWAPART +
                             (MKOOPKLA > 5) +
                             MOPLLAAG +
#                             MHKOOP +
#                             MHHUUR +
#                             MINKM30 +
#                             MAUT0 +
                             MRELGE +
#                             MBERARBO +
#                             MFALLEEN +
                             MAUT1,
                         family = binomial)

summary(ticDataLogitModel)
anova(ticDataLogitModel, test="Chisq")

ticDataTrainingPrediction <- predict(ticDataLogitModel, type = "response")
summary(ticDataTrainingPrediction)
table(ticDataTraining$CARAVAN, ticDataTrainingPrediction > 0.14)
tapply(ticDataTrainingPrediction, ticDataTraining$CARAVAN, mean)

ticDataTraining$Prediction <- ticDataTrainingPrediction

ticDataTestPrediction <- predict(ticDataLogitModel, newdata = ticDataTest, type= "response")
table(ticDataTest$CARAVAN, ticDataTestPrediction > 0.11)
tapply(ticDataTestPrediction, ticDataTest$CARAVAN, mean)

ggplot(ticDataTraining, aes(x = CARAVAN, y = Prediction, fill = CARAVAN)) +
    geom_boxplot() +
    scale_y_continuous(breaks = seq(0,1,0.05)) +
    theme_bw()
```