---
title: "EDA Single Variable Exercise"
author: "Vivek Appadurai"
date: "February 17, 2016"
output:
    html_document:
        keep_md: true
---

# R Markdown Document to Explore Price Per Carat of Diamonds Across Different Colors

### Using dplyr and ggplot2 packages for data maniulation and plotting

Using the Diamonds Dataset

```{r, message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
data(diamonds)
```

### Glimpse of the diamonds dataset

```{r}
glimpse(diamonds)
```

### Checking for the number of distinct colors and plotting a histogram of colors

Color G is most common 

Color J is least common

```{r}
diamonds %>%
    group_by(color) %>%
    summarize(count = n())

ggplot(data = diamonds, aes(x = color, fill = color)) +
    geom_histogram() +
    theme_bw()
```

### Create an additional column in the diamonds dataset by calculating price per carat using dplyr mutate

```{r}
diamonds <- diamonds %>% 
    mutate(price_per_carat = price/carat)
```

### Plotting a histogram of price per carat faceted by color with the median price per carat indicated

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(diamonds, aes(x = price_per_carat, fill = color)) + 
    geom_histogram() + 
    theme_bw() + 
    facet_wrap(~color, ncol = 2) + 
    geom_vline(linetype = "dotted", aes(xintercept = median(diamonds$price_per_carat)))
```

### Generating a Boxplot to explore relationship between color and price per carat of diamonds

Color H appears to have the highest median price/carat

Colors D, E, F appear to have most outliers

Color G has the largest interquartile range

```{r, echo=FALSE}
ggplot(diamonds, aes(x = color, y = price_per_carat, fill = color)) + 
    geom_boxplot() + 
    theme_bw()
```

### Creating text summaries of price per carat based on color

```{r}
by(diamonds$price_per_carat, diamonds$color, summary)
```