---
title: "EDA Multiple Variabel Exercise"
author: "Vivek Appadurai"
date: "February 21, 2016"
output: 
    html_document:
        keep_md: true
---

### Loading Libraries

```{r, message = FALSE}
library(ggplot2)
library(dplyr)
data(diamonds)
```

### Plotting histogram of diamond prices, faceted by color, filled by cut

```{r}
ggplot(diamonds, aes(x = price, fill = cut)) + 
    geom_histogram(binwidth = 100) + 
    facet_wrap(~ color) + 
    theme_bw()
```

### Plotting price vs table, fill by cut

```{r}
ggplot(diamonds, aes(x = table, y = price, color = cut)) + 
    geom_point() + 
    scale_x_continuous(breaks = seq(0, 100, 2)) +
    theme_bw()
```

### Creating a Volume Column, plotting price vs volume, colored by clarity, omitting top 1 percentile volume diamonds

```{r, warning = FALSE}
diamonds <- diamonds %>%
    mutate(volume = x * y * z)

ggplot(diamonds, aes(x = volume, y = price, color = clarity)) + 
    geom_point() + 
    scale_x_continuous(limits = quantile(diamonds$volume, c(0,0.9))) +
    theme_bw()
```

Creating a new variable prop_initiated in pseudo facebook dataframe using dplyr, mutate and ifelse statement

```{r}
pf <- read.delim('pseudo_facebook.tsv')
pf <- pf %>% 
    mutate(prop_initiated = ifelse(friend_count > 0, friendships_initiated / (friend_count), 0))
pf %>% head()
```

Creating a new year joined variable in pseudo facebook data, binning the data by years and plotting tenure vs proportion of friendships initiated, colored by year joined bin and smoothing

```{r}
pf <- pf %>% mutate(year_joined = floor(2014 - tenure/365))

pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))

ggplot(pf, aes(x = tenure, y = prop_initiated, color = year_joined.bucket)) +
    geom_smooth(stat = 'summary', fun.y = 'median') +
    theme_bw()

pf %>% group_by(year_joined.bucket) %>%
    summarise(mean = mean(prop_initiated))
```

Plotting cut vs price to carat ratio of diamonds, colored by diamond color, faceted by clarity, rotating axis labels for better visualization

```{r}
ggplot(diamonds, aes(x = cut, y = price/carat, color = color)) +
    geom_jitter() +
    facet_wrap(~ clarity) +
    theme(axis.text.x = element_text(angle = 90)) +
    theme_bw()
```